---
title: "Codefocus Example"
format:
  revealjs: default
revealjs-plugins:
  - codefocus
execute:
  echo: true
embed-resources: true
---

# Slide One

```{r}
vector <- c(1,2,3)
vector <- sample(vector)
sum(vector)
```

::: {.fragment .current-only data-code-focus="1"}
When this fragment is shown, the first line of code will have the `focus` class added to it and it gets highlighted.
:::

::: {.fragment .current-only data-code-focus="2"}
Another fragment. This time, both lines will now have the `focus` class.
:::

::: {.fragment .current-only data-code-focus="1,3"}
And now both 1 and 3.
:::

## Slide two 
```{r}
a <- 1
b <- 2
c <- b + a
```
and, 

```{r}
print(c)
```

::: {.fragment .current-only data-code-focus="1-2"}
Here we have declared two variables
:::

::: {.fragment .current-only data-code-focus="3"}
Then added them and passed them to c
:::

::: {.fragment data-code-focus="1" data-code-block="2"}
Then print the c
:::

## Using normal highlights
You can still use normal higlights as well. 
```{.r code-line-numbers="1,3|2"}
a <- 1
b <- 2
c <- 1 + 2
```